ODGI: scalable tools for pangenome graphs

### 2021-06-01 manuscript/main.tex
Bib works

@@

@@

    \topic{odgi build, view \& validate} pangenome graphs can be
    stored in the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFAv1}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and \textit{vice versa}.
    \cmd{odgi validate} ascertains the graph data is correct, such as
    validating that paths respect the graph's topology.

@@

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
      \processtable{Example of performance improvement between
        \cmd{odgi} and \cmd{VG} equivalent commands with output file
        sizes. The centromere region was extracted from CHR 6 of the
        HPRC year one assembly\citep{HPRC}, i.e., 88 haploid, phased
        human genome assemblies from 44 individuals plus the chm13
        cell line and GRCh38 reference genomes stored in 4.3GB GFA
        format.
        %
        First GFS was converted from GFA to \odgi\ and \cmd{vg}
        formats, respectively.  \odgi's path implementation can
        process paths in parallel, outperforming \cmd{vg}. For the
        same reason \cmd{odgi extract} is $20\times$ faster than
        \cmd{vg chunk} extracting a portion from the full
        graph. \FIXME: vg never finished.
        %
        All timings were performed on a server class machine
        on SSD MODEL with X GB of RAM and 48 CPU cores (Y x 12 core
        AMD Opteron) Processor MODEL @ 3.3 GHz with 8MB L2
        Cache.\FIXME
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}

@@

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

    %ToDo
    \begin{thebibliography}{}

        \bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
        Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.

        \bibitem[Bag {\it et~al}., 2001]{Bag01}
        Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.

        \bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
        Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
        in nigral dopaminergic neurnol cell: correlation with the known
        pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
        Res.}, \textbf{110}(Suppl. 1), 76--84.

        \bibitem[Lehmann, 1986]{Leh86}
        Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.

        \bibitem[Crenshaw and Jones, 2003]{Cre03}
        Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
        cancer management: one tumor, one chip. \textit{Bioinformatics},
        doi:10.1093/bioinformatics/btn000.

        \bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
        Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
        (ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
        ???--???.

        \bibitem[Bardet, 1920]{Bar20}
        Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
        polydactylie et retinite pigmentaire (contribution a l'etude des
        formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
        institution, Paris, France.

    \end{thebibliography}
\end{document}

>>>>

\usepackage{natbib}

@@

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
      \processtable{Example of performance improvement between
        \cmd{odgi} and \cmd{VG} equivalent commands with output file
        sizes. The centromere region was extracted from CHR 6 of the
        HPRC year one assembly\citep{HPRC}, i.e., 88 haploid, phased
        human genome assemblies from 44 individuals plus the chm13
        cell line and GRCh38 reference genomes stored in 4.3GB GFA
        format\citep{GFA}.
        %
        First GFS was converted from GFA to \odgi\ and \cmd{vg}
        formats, respectively.  \odgi's path implementation can
        process paths in parallel, outperforming \cmd{vg}. For the
        same reason \cmd{odgi extract} is $20\times$ faster than
        \cmd{vg chunk} extracting a portion from the full
        graph. \FIXME: vg never finished.
        %
        All timings were performed on a server class machine
        on SSD MODEL with X GB of RAM and 48 CPU cores (Y x 12 core
        AMD Opteron) Processor MODEL @ 3.3 GHz with 8MB L2
        Cache.\FIXME
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}

@@

    \topic{odgi build, view \& validate} pangenome graphs can be
    stored in the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFA}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and \textit{vice versa}.
    \cmd{odgi validate} ascertains the graph data is correct, such as
    validating that paths respect the graph's topology.

@@

@@

\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

\bibliography{bibliography}

\end{document}
